Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-16 paper/flairs27/paper.tex
Worked on the discussion version of the paper, added lots of comments
added a conclusion section
Made small changes to the paper.tex to prepare for submission

\newcommand\ceg[1]{\textcolor{red}{#1}} % Red marker to declare errors.

@@

\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
       \\
       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
       {mpetrovic@ihmc.us}
}

@@

%\input{content/conclusion.tex}

\section*{Acknowledgements}
We would like to thank John Frank and TREC for providing the data set.
Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.

>>>>

\newcommand\ceg[1]{\textcolor{red}{#1 -- CEG}} % Red marker to declare errors.
\newcommand\hide[2]{#2}

@@

%\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
%       \\
%       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
%       {mpetrovic@ihmc.us}
%}
\author{XXX}

@@

\input{content/conclusion.tex}

\section*{Acknowledgements}
We would like to thank \hide{John Frank}{XXX} and \hide{NIST}{XXX} for providing the data set.
\hide{Christan Grant}{XXXX} is funded by \hide{a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270}{XXXX}.
